Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-10-06 paper/paper_main.tex
affliation change for James

\author{James W. Gardner}
\email{u6069809@anu.edu.au}
\affiliation{%
College of Science, Australian National University, Acton, ACT, 2601, Australia 
}%
\affiliation{%
 School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}

>>>>

\author{James W. Gardner}
\email{u6069809@anu.edu.au}
% \affiliation{%
% College of Science, Australian National University, Acton, ACT, 2601, Australia 
% }%
\affiliation{%
ANU Centre for Gravitational Astrophysics, The Australian National University, Acton, ACT, 2601, Australia
}
\affiliation{%
OzGrav-ANU, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, The Australian National University, Acton, ACT, 2601, Australia
} 
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
